rowing: analysis of sculls in the 2016 Olympics

### 2022-11-22 inst/rowing.Rmd
rowing_minimal_table

```{r rowingminimaldef}
o <- sapply(readLines("rowing_minimal.txt"),strsplit," ")
names(o) <- NULL  
rowing_minimal  <- Reduce("+",sapply(o,race))
summary(rowing_minimal)
```

@@

```{r,label=saverowingingdataset}
save(rowing,rowing_minimal,rowing_maxp,rowing_minimal_maxp,rowing_table,file="rowing.rda")
```

>>>>

```{r rowingminimaldef}
rowing_minimal_table <- sapply(readLines("rowing_minimal.txt"),strsplit," ")
names(rowing_minimal_table) <- NULL  
rowing_minimal  <- Reduce("+",sapply(rowing_minimal_table,race))
summary(rowing_minimal)
```

@@

```{r,label=saverowingingdataset}
save(rowing,rowing_minimal,rowing_maxp,rowing_minimal_maxp,rowing_table,rowing_minimal_table,file="rowing.rda")
```
